Minimizing post-shock forecasting error using disparate information

### 2020-06-09 manuscript/manuscript.tex
made a round of updates to the manuscript

% title
\title{Minimizing post shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Ziyu Liu\thanks{ziyuliu3@illinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate 
    time series that have undergone similar shocks for which post-shock 
    outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction. Parametric bootstrap procedures are provided for such realization. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. From a machine learning perspective, \citet{agarwal2020two} proposed a model-free synthetic intervention  method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions.

@@

We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), 
$t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a 
scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to 
the analyst prior to the observation of $y_{1,t}$.  Suppose that the analyst 
is interested in forecasting $y_{1,t}$, the first time series in the 
collection.
%$y_1, y_2, \ldots$.  
%Given each time point $t \geq 1$, let $\x_{1,t}$ be a vector of covariates 
%revealed prior to the observation of $y_{1,t}$.  
To gauge the performance of a procedure that produces forecasts 
$\{\hat y_{1,t}, t= 1,2,\ldots\}$ given time horizon $T_1$, 
we consider forecast risk in the form of  mean squared error (MSE),
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
$$
in our analyses. In this article, we consider a dynamic panel data 
model with autoregressive structure similar to that in \citet{blundell1998initial}. 
%without past time period covariate 
%information and with a single present time covariate.  
Our dynamic panel model includes an additional shock effect whose presence 
or absence is given by the binary variable $D_{i,t}$, the details of this model 
are in the next section.

@@

@@

\alpha_i &\simiid  \normal{\mu_{\alpha}}{\sigma^2_{\alpha}}, \qquad  i = 1, \ldots, n+1; \\

@@

In this section, we present a bootstrap procedure 
%(see Section \ref{modelsetup}) 
that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible parametric bootstrap procedures for our methods, one conditioned on donor pool and the other  without. We first illustrate the simpler parametric bootstrap conditioned on the donor pool. The formal steps of it are outlined in the Supplementary Materials, the intuition for our procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

The parametric bootstrap without conditioning on the donor pool differs from the one with in the step that the former performs a non-parametric bootstrap by sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$.

@@

\subsection{Parametric bootstrap simulation for risk-reduction propositions}
\label{parametricbootstrapsimulation}

@@

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Accept $\hat{\alpha}$ & Reject $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}
In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6th, 2020, the Friday before the stock market crash on March 9th, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustment for the shock. The forecast consists of four steps: (1) pick a model, (2) selection of covariates,  (3) choices of donor pool. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

\begin{enumerate}
\item[(1)] {\bf AR(1) model and time window}. We will use a simple AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of 1 and 3 months \citep{alquist2013forecasting}. We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed after September 11th, 2001, %March 18th, 2008, 
several events in September, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}. The reasons for those three shocks are:
  \begin{enumerate}
  \item On September 11th, 2001, Islamic extremist al-Qaeda committed a series of terrorist attacks against the United States of America \citep{braniff2011towards}. In addition to the tragic loss of life, this triggered negative repercussions on the U.S. and world economies with falling stock prices and a falling U.S. dollar \citep{floyd2001terror}. Moreover, trading was closed until September 17, 2001 \citep{johnston2006impact}.
  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
  \end{enumerate}
%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
We assume that the five shocks are independent of the shock that Conoco Phillips  experienced on 2020-03-09. The covariates and response of time series in the donor pool are adjusted for inflation.
\end{enumerate}

@@

%Some other notable shock effects were not included in this analysis because the conditions preceding them are not similar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects \citep{shiller1988portfolio, latimes, nytimes}.

@@

\vspace{-.3cm}
\begin{table}[H]
  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
  \begin{center}
    \begin{tabular}{ccrrrrrr}
       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
             \hline 
2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
  2008 Mar.  & 03--17 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
 \multirow{3}{*}{2008 Sep.}
 & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
 & $T_4^* +1 = \text{09--12}$ \\
   & $T_5^* +1 = \text{09--26}$ \\
\\
  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
    \end{tabular}
  \end{center}  \vspace{-.3cm}
\end{table}

Table \ref{table1} presents some basic summary statistics for the covaraites and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool. Note that there are three shock-effects nested in the time series 2008 September. This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool. Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.

We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. Table \ref{table1} that contains some basic summary statistics for the units and range of the covariates can provide some information about the performance of the fit. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately.

$\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (2008--09--08) and $\alpha_5$ (2014--11--27) according to the setup of $\mc{M}_2$. That is, the shock that Conoco Phillips experienced in 2020-03-09 is similar to the shock induced by the placement of Fannie May and Freddie Mac, and the one caused by oil supply shock on 2014--11--27. It is consistent with discussion at the beginning of the section.
\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1 \\
    Best shock-effect estimator & 0 & 1 & 0
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

@@

We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27th, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.797$, $2.812$, and $0.437$, respectively.

These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding. Our apriori justification comes from \citet{kilian2009not} who study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.

However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest. The shock on 2020-03-09 occurred with the pandemic caused by  COVID-19. It is difficult to find available stock market time series data that were generated under a similar setting.

>>>>

% title
\title{Minimizing post-shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Ziyu Liu\thanks{ziyuliu3@illinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works, and which estimator is the best in average forecast risk reduction. Bootstrap procedures are provided to estimate the variability of our shock effect estimators and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

Data integration for forecasting is a broad area of research including ideas from many areas. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be beneficial for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
\citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool.

@@

We will suppose that an analyst has time series data ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$, where $y_{i,t}$ is a scalar response and $\x_{i,t}$ is a vector of covariates that are revealed to the analyst prior to the observation of $y_{1,t}$.  Suppose that the analyst is interested in forecasting $y_{1,t}$, the first time series in the collection. 
%$y_1, y_2, \ldots$.  
%Given each time point $t \geq 1$, let $\x_{1,t}$ be a vector of covariates 
%revealed prior to the observation of $y_{1,t}$.

We will suppose that specific interest is in forecasts to made after the occurrence of a structural shock. To gauge the performance of forecasts, we consider forecast risk in the form of mean squared error (MSE),
$$
  R_T = \frac{1}{T}\sum_{t=1}^T\E{\hat y_{1,t} - y_{1,t}}^2,
$$
and root mean squared error (RMSE), given by $\sqrt{R_T}$, in our analyses.

%The forecast consists of three steps: (1) pick a model, (2) selection of covariates, (3) choices of donor pool.
Our post-shock prediction methodology will consist of selecting covariates $x_{i,t}$, constructing a suitable donor pool of candidate time series that have undergone similar structural shocks to the time series under study, and specifying a model for the time series ($y_{i,t}$,$\x_{i,t}$), $t = 1$, $\ldots$, $T_i$, $i = 1$, $\ldots$, $n+1$. In this article, we consider a dynamic panel data model with autoregressive structure similar to that in \citet{blundell1998initial}. Our dynamic panel model includes an additional shock effect whose presence or absence is given by the binary variable $D_{i,t}$, and we will assume that the donor pool time series are independent of the time series under study. The details of this model are in the next section.

@@

\alpha_i &\simiid \alpha, \where \E{\alpha}=\mu_{\alpha}, \var{\alpha}=\sigma_{\alpha}^2, \qquad  i = 1, \ldots, n+1; \\

@@

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators and check the underlying conditions of our risk reduction results in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

To specify, there are two possible bootstrap procedures for our methods, one based on resampling the donor pool with replacement and the other without any resampling of the donor pool. We first illustrate the simple bootstrap without resampling the donor pool. The formal steps of it are outlined in the Supplementary Materials, the intuition for this procedure is as follows: let $B$ be the bootstrap sample size and let $I=\{2, \ldots, n +1\}$ be the indexes for donor pool. initialize $y_{i,0}$ for all $i \in I$. At iteration $b$, resample the residuals and then obtain shock-effect estimators for each of the disparate time series for all $i \in I$. Then construct and store any of the adjustment estimators $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$. We can then estimate distributional quantities of our shock-effect estimators with the bootstrap sample of $\hat{\alpha}^{(b)}_{\mrm{adj}}$, $\hat{\alpha}^{(b)}_{\mrm{wadj}}$, and $\hat{\alpha}^{(b)}_{\mrm{IVW}}$, for $b = 1,\ldots,B$.
%The errors $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$ for $t \in \{1, \ldots, T_i^*\}$ and $t' \in \{T_i^*+1, \ldots, T_i\}$ are iid. 
%since $y_{i,t}$ differs from $y_{i,t'}$ only in the shock-effect $\alpha_i$ conditioned on $\Theta$, and it is not absorbed into $\varepsilon_{i,t}$ and $\varepsilon_{i,t'}$. Therefore, this parametric bootstrap framework will work for us.
Once can then use the bootstrapped shock-effects estimated by our residual bootstrap to provide an approximation for parameters involved in the risk-reduction conditions in Propositions \ref{proprisk} and \ref{propriskwadj2}.

The bootstrap based on resampling the donor pool with replacement is the same as above with the addition of first round of sampling $n$ values from $I=\{2, \ldots, n+1\}$ without replacement to generate  $I^*$. Then, it follows the same step with the one conditioned on the donor pool by replacing $I$ by $I^*$. Care is needed when using this bootstrap procedure to estimate the variability of $\hat{\alpha}_{\mrm{wadj}}$. When the rank of the design matrix corresponding to the mean function of $\alpha_i$ under $\mc{M}_2$ is greater than $n$ then our bootstrap procedure will work fine, however, if the constraints used to obtain $\mathbf{W}^*$ are binding then our bootstrap procedure needs to be modified \citep{li2019statistical}. The subsampling method in Section 4 of \citet{li2019statistical} can be adapted to our post-shock setting when the constraints are binding.

@@

\subsection{Bootstrap simulation for risk-reduction propositions}
\label{parametricbootstrapsimulation}

@@

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise.

@@

\section{Forecasting Conoco Phillips stock in the presence of shocks}
\label{forecasting}
In this example we forecast Conoco Phillips stock prices in the midst of the coronavirus recession. Specific interest is in predictions made after March 6, 2020, the Friday before the stock market crash on March 9, 2020. We will detail how we combine knowledge from disparate time series to improve the forecast of Conoco Phillips stock price that would be made without adjustments for the shock. %Section \ref{background} provides the justification for the first three steps. Section \ref{results} discusses the result of our forecast.

@@

\begin{enumerate}
\item[(1)] {\bf AR(1) model and time window}. We will use an AR(1) model to forecast Conoco Phillips stock price. This model has been shown to beat no-change forecasts when predicting oil prices over time horizons of one and three months \citep{alquist2013forecasting}. We will consider 30 pre-shock trading days and we will forecast the immediate shock effect and the shock effect over a future five trading day window. All estimates will be adjusted for inflation. The model setup for AR(1) is exactly the same as what is stated in Section \ref{modelsetup} with addition of shock effects. All the parameters are estimated using OLS.
\item[(2)] {\bf Selection of covariates}. We perform our analyses incorporating daily S\&P 500 index prices and West Texas Intermediate (WTI) crude oil prices as covariates. 
\item[(3)] {\bf Construction of donor pool}. Our donor pool will consist of Conoco Phillips shock effects observed on March 14, 2008, several events in September, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yield curve \citep{bauer2018economic}, and the third was an OPEC induced supply side shock effect \citep{huppmann2015opec}. The reasons for those three shocks are:
  \begin{enumerate}
  \item On March 14, 2008, Bear Stearns was verging on bankruptcy from what its officials described as a sudden liquidity squeeze related to its large exposure to devalued mortgage-backed securities. On that day, it also received word that it was getting an unprecedented loan from the Federal Reserve System, this decision was unprecedented: never before had the Fed committed to ``bailing out'' a financial entity that was not a commercial bank. The day of the announcement, the stocks of other major Wall Street firms tumbled (including Conoco Phillips). These concerns then spilled over into the broader universe of stocks \citep{shorter2008bear}. %In heavy trading on Tuesday, March 18, the firm’s share price closed at \$5.91.
  \item  In early September 2008, time series of oil prices experienced a sudden increase in volatility simultaneously due to turmoil in financial markets. The political, economic, social or environmental events may coincide with these shocks \citep{ewing2013volatility}. Notable shock effects followed the placement of Fannie May and Freddie Mac in conservatorship on September 7th (shock effect on the 8th), Lehman Brothers filing for bankruptcy on September 15th, and the Office of Thrift Supervision closes Washington Mutual Bank on September 25th \citep{dwyer2009financial, longstaff2010subprime}.
  \item On November 27th, 2014, it is documented that oil prices fall as OPEC opts not to cut production \citep{huppmann2015opec}. During the Great Recession when economic activity clearly declined, both oil and stock prices fell which points to demand factors. During the second half of 2014, oil prices plummeted but equity prices generally increased, suggesting that supply factors were the key driver \citep[Page 19]{baffes2015great}. 
  \end{enumerate}
%\item[(4)] {\bf Forecast}. \textbf{Jilei, please fill this in. I do not know what you have in mind.}
\end{enumerate}

@@

@@

%\vspace{-.3cm}
%\begin{table}[H]
%  \caption{Some basic summary statistics of the covariates and response} \vspace{.4cm} \label{table1}
%  \begin{center}
%    \begin{tabular}{ccrrrrrr}
%       &    & \multicolumn{2}{c}{S\&P 500} & \multicolumn{2}{c}{WTI}  & \multicolumn{2}{c}{$y_{i,t}$} \\
%     Time series & $T_i^*+1$ & Mean & SD  &  Mean & SD  & Mean & SD  \\
%             \hline 
%2020 Mar.  &  03--09 & 3239.11 & 139.28 & 50.36 & 3.13 & 55.35 & 6.37 \\ 
%  2008 Mar.  & 03--14 & 1341.03 & 29.50 & 98.82 & 7.01 & 60.59 & 2.28 \\ 
% \multirow{3}{*}{2008 Sep.}
% & $T_3^* +1 = \text{09--08}$ & \multirow{3}{*}{1504.50}  & \multirow{3}{*}{43.44}  & \multirow{3}{*}{134.46} & \multirow{3}{*}{10.24} & \multirow{3}{*}{71.20}  & \multirow{3}{*}{4.11}  \\ 
% & $T_4^* +1 = \text{09--12}$ \\
%   & $T_5^* +1 = \text{09--26}$ \\
%\\
%  2014 Nov.  & 11--27 & 2179.99 & 66.99 & 85.70 & 3.38 & 76.99 & 1.90 \\ 
%    \end{tabular}
%  \end{center}  \vspace{-.3cm}
%\end{table}

%Table \ref{table1} presents some basic summary statistics for the covariates and response for the time series of interest (stock price of Conoco Phillips in 2020 March) and the donor pool.

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.949, 0.000, 0.051) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 23.496.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The fit is acceptable. According to discussions in Section \ref{constructionofestimators}, the property of $\hat{\alpha}_{\rm wadj}$ should hold approximately. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is similar to $\alpha_3$ (September 8, 2008) and $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped mean  & $-5.340$ & $-5.014$ & $-5.287$ \\
    Bootstrapped variance & 0.508 & 0.480 & 2.821 \\
    Risk-reduction proposition & 1 & 1 & 1
%    Best shock-effect estimator & 0 & 1 & 0
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

@@

We also study additive shock effect estimators where the shock effects corresponding to separate supply and demand shocks are added to estimate the unknown shock effect. The supply shock donor pool consists of the November 27, 2014 shock effect and the demand shock donor pool consists of the remaining shock effects. The additive adjustment estimator computed by adding the $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{adj}}$, and $\hat{\alpha}_{\text{IVW}}$ estimators for the demand and supply shock effects have  MSEs of $1.797$, $2.812$, and $0.437$, respectively. These additive adjustment estimators do extremely well, nearly perfectly forecasting the realized shock effect. There is apriori justification for the use of these simply additive adjustment estimators, although their nearly perfect performance in this example is a retrospective finding. Our apriori justification comes from \citet{kilian2009not} who study the effect that different supply and demand shocks have on oil prices through a vector auto regressive model. Their model postulates an additive nature of shock effects, although the additivity parameters requires estimation in their context. %This provides some anecdotal justification for apriori estimation of the March 9th Conoco Phillips shock effect with the addition of the adjustment estimator corresponding to the separate supply and demand aspects of this shock effect.

However, from another perspective, this phenomenon can be explained by the fact that the donor pool is not constructed to be similar enough to the time series of interest. The shock(s) on March 9, 2020 in the midst of the COVID-19 pandemic and oil production volatility. It is difficult to find available stock market time series data that were generated under a similar setting.
